\footnotesize
\begin{longtable}{@{}l l l l l c l@{}}
\caption{Full extracted-studies corpus (217 included studies). Agreement is the headline coefficient/proportion where reported.}\label{tab:full}\\
\toprule
Key & Study & Domain & Task & Metric & Agree & Verdict \\
\midrule
\endfirsthead
\toprule Key & Study & Domain & Task & Metric & Agree & Verdict \\ \midrule \endhead
\texttt{mirzakhmedova2024argument} & Mirzakhmedova et al. (2024) & Argument Quality & pointwise & pct\_agreement & - & Mixed \\
\texttt{tong2024codejudge} & Tong et al. (2024) & Code \& SW Eng & classify & accuracy & - & Promising \\
\texttt{watson2024aicodereview} & Watson et al. (2024) & Code \& SW Eng & classify & pct\_agreement & - & Mixed \\
\texttt{codespec2025} & Jin et al. (2025) & Code \& SW Eng & verify & accuracy & - & Caution \\
\texttt{wang2025setesting} & Wang et al. (2025) & Code \& SW Eng & pairwise & pct\_agreement & - & Mixed \\
\texttt{zhuo2025codejudgeeff} & Wang et al. (2025) & Code \& SW Eng & pointwise & kappa & - & Mixed \\
\texttt{biasloop2026} & Zhao et al. (2026) & Code \& SW Eng & pairwise & pct\_agreement & - & Caution \\
\texttt{overcorrect2026} & Jin et al. (2026) & Code \& SW Eng & classify & accuracy & - & Caution \\
\texttt{hatespeechprobe2023} & Roy et al. (2023) & Content Moderation \& Toxicity & classify & f1 & - & Mixed \\
\texttt{li2023hotchatgpt} & Li et al. (2023) & Content Moderation \& Toxicity & classify & pct\_agreement & - & Mixed \\
\texttt{nguyen2024crisismisinfo} & Nguyen \& Rudra (2024) & Content Moderation \& Toxicity & classify & f1 & - & Mixed \\
\texttt{hatespeechanno2025} & authors (2025) & Content Moderation \& Toxicity & classify & kappa & - & Caution \\
\texttt{icwsm2025hatebias} & Giorgi et al. (2025) & Content Moderation \& Toxicity & classify & kappa & - & Caution \\
\texttt{xie2023nextchapter} & Xie et al. (2023) & Creative Writing & pointwise & pct\_agreement & - & Mixed \\
\texttt{chakrabarty2024artartifice} & Chakrabarty et al. (2024) & Creative Writing & pointwise & pearson & 0.10 & Unreliable \\
\texttt{ismayilzada2024creative} & Ismayilzada et al. (2024) & Creative Writing & pointwise & pct\_agreement & - & Caution \\
\texttt{creativeevalmdpi2025} & Kim et al. (2025) & Creative Writing & pointwise & spearman & - & Mixed \\
\texttt{haase2025creativitypeaked} & Haase et al. (2025) & Creative Writing & pointwise & pct\_agreement & - & Caution \\
\texttt{litbench2025} & Fein et al. (2025) & Creative Writing & pairwise & pct\_agreement & 0.78 & Mixed \\
\texttt{lin2023llmeval} & Lin \& Chen (2023) & Dialogue & pointwise & spearman & - & Promising \\
\texttt{mendonca2024dialogue} & Mendonca et al. (2024) & Dialogue & pointwise & spearman & - & Mixed \\
\texttt{hackl2023reliablerater} & Hackl et al. (2023) & Education \& Grading & pointwise & icc & - & Promising \\
\texttt{khademi2023bardassessment} & Khademi (2023) & Education \& Grading & pointwise & pct\_agreement & - & Mixed \\
\texttt{kortemeyer2023physics} & Kortemeyer (2023) & Education \& Grading & pointwise & pct\_agreement & - & Mixed \\
\texttt{mizumoto2023aes} & Mizumoto \& Eguchi (2023) & Education \& Grading & pointwise & qwk & 0.74 & Promising \\
\texttt{yancey2023cefr} & Yancey et al. (2023) & Education \& Grading & pointwise & qwk & - & Mixed \\
\texttt{aescomparative2024} & Lee et al. (2024) & Education \& Grading & pointwise & qwk & 0.57 & Mixed \\
\texttt{floden2024gradingexams} & Flodén (2024) & Education \& Grading & pointwise & pct\_agreement & - & Mixed \\
\texttt{grevisse2024asagmed} & Grévisse (2024) & Education \& Grading & classify & pct\_agreement & - & Promising \\
\texttt{hou2024classroom} & Hou et al. (2024) & Education \& Grading & pointwise & icc & - & Mixed \\
\texttt{k12shortanswer2024} & Henkel et al. (2024) & Education \& Grading & classify & kappa & 0.70 & Promising \\
\texttt{koraishi2024langassess} & Koraishi (2024) & Education \& Grading & pointwise & pct\_agreement & - & Mixed \\
\texttt{quah2024dentalaes} & Quah et al. (2024) & Education \& Grading & pointwise & icc & - & Mixed \\
\texttt{wang2024beyondagreement} & Wang et al. (2024) & Education \& Grading & pointwise & qwk & - & Mixed \\
\texttt{writingmultidim2024} & Steiss et al. (2024) & Education \& Grading & pointwise & qwk & - & Promising \\
\texttt{asagfair2025} & Henkel et al. (2025) & Education \& Grading & pointwise & kappa & - & Mixed \\
\texttt{sefl2025feedback} & authors (2025) & Education \& Grading & pointwise & f1 & - & Promising \\
\texttt{studentsjudge2025} & Banihashem et al. (2025) & Education \& Grading & pointwise & pct\_agreement & - & Mixed \\
\texttt{k12sci2026} & He et al. (2026) & Education \& Grading & pointwise & pct\_agreement & - & Promising \\
\texttt{claimmatch2023} & Choi et al. (2023) & Fact-Checking & classify & pct\_agreement & - & Promising \\
\texttt{ni2024afacta} & Ni et al. (2024) & Fact-Checking & classify & pct\_agreement & - & Promising \\
\texttt{politicaltruths2024} & Chatrath et al. (2024) & Fact-Checking & classify & pct\_agreement & - & Mixed \\
\texttt{factsopinions2025} & Saju et al. (2025) & Fact-Checking & classify & accuracy & - & Caution \\
\texttt{kaikaus2023financecorpora} & Kaikaus et al. (2023) & Finance & classify & accuracy & - & Mixed \\
\texttt{bizfinbench2025} & Lu et al. (2025) & Finance & pointwise & pct\_agreement & - & Mixed \\
\texttt{trident2025} & Hui et al. (2025) & Finance & classify & pct\_agreement & - & Mixed \\
\texttt{chan2023chateval} & Chan et al. (2023) & General NLG & pairwise & pct\_agreement & - & Mixed \\
\texttt{chiang2023alt} & Chiang \& Lee (2023) & General NLG & pointwise & pct\_agreement & - & Mixed \\
\texttt{dubois2023alpacafarm} & Dubois et al. (2023) & General NLG & pairwise & winrate\_corr & 0.98 & Promising \\
\texttt{hsu2023figurecaption} & Hsu et al. (2023) & General NLG & pointwise & spearman & - & Promising \\
\texttt{kim2023prometheus} & Kim et al. (2023) & General NLG & pointwise & pearson & 0.90 & Promising \\
\texttt{lai2023styletransfer} & Lai et al. (2023) & General NLG & pointwise & spearman & - & Mixed \\
\texttt{li2023autoj} & Li et al. (2023) & General NLG & pairwise & pct\_agreement & - & Mixed \\
\texttt{wang2023chatgptnlg} & Wang et al. (2023) & General NLG & pointwise & spearman & - & Mixed \\
\texttt{wang2023pandalm} & Wang et al. (2023) & General NLG & pairwise & accuracy & - & Promising \\
\texttt{xu2023instructscore} & Xu et al. (2023) & General NLG & pointwise & pearson & - & Promising \\
\texttt{zhang2023widerdeeper} & Zhang et al. (2023) & General NLG & pairwise & pct\_agreement & - & Mixed \\
\texttt{zheng2023mtbench} & Zheng et al. (2023) & General NLG & pairwise & pct\_agreement & 0.85 & Validated \\
\texttt{chiang2024arena} & Chiang et al. (2024) & General NLG & pairwise & pct\_agreement & - & Validated \\
\texttt{doostmohammadi2024autoeval} & Doostmohammadi et al. (2024) & General NLG & pointwise & pct\_agreement & - & Mixed \\
\texttt{dubois2024lc} & Dubois et al. (2024) & General NLG & pairwise & winrate\_corr & 0.98 & Promising \\
\texttt{hashemi2024llmrubric} & Hashemi et al. (2024) & General NLG & pointwise & pearson & - & Promising \\
\texttt{huang2024nlexpl} & Huang et al. (2024) & General NLG & pointwise & pct\_agreement & - & Mixed \\
\texttt{kim2024prometheus2} & Kim et al. (2024) & General NLG & pointwise & pearson & - & Promising \\
\texttt{li2024arenahard} & Li et al. (2024) & General NLG & pairwise & pct\_agreement & 0.89 & Promising \\
\texttt{lin2024wildbench} & Lin et al. (2024) & General NLG & pairwise & winrate\_corr & 0.98 & Promising \\
\texttt{verga2024poll} & Verga et al. (2024) & General NLG & pairwise & pct\_agreement & - & Promising \\
\texttt{faggioli2023perspectives} & Faggioli et al. (2023) & IR \& Relevance & classify & kappa & - & Promising \\
\texttt{alaofi2024fooledrelevant} & Alaofi et al. (2024) & IR \& Relevance & classify & pct\_agreement & - & Caution \\
\texttt{clarke2024cantreplace} & Clarke \& Dietz (2024) & IR \& Relevance & classify & kappa & - & Caution \\
\texttt{thomas2024relevance} & Thomas et al. (2024) & IR \& Relevance & classify & kappa & - & Validated \\
\texttt{upadhyay2024largescale} & Upadhyay et al. (2024) & IR \& Relevance & classify & kappa & - & Promising \\
\texttt{zhuang2024beyondyesno} & Zhuang et al. (2024) & IR \& Relevance & ranking & kendall & - & Promising \\
\texttt{arabzadeh2025benchrelevance} & Arabzadeh \& Clarke (2025) & IR \& Relevance & classify & kappa & - & Mixed \\
\texttt{arabzadeh2025promptsens} & Arabzadeh \& Clarke (2025) & IR \& Relevance & classify & kappa & - & Mixed \\
\texttt{frobe2025assessorsagree} & Frobe et al. (2025) & IR \& Relevance & classify & kappa & - & Caution \\
\texttt{li2023coannotating} & Li et al. (2023) & Information Extraction (NER/NLI) & classify & pct\_agreement & - & Promising \\
\texttt{humanllmcollab2024} & Wang et al. (2024) & Information Extraction (NER/NLI) & classify & pct\_agreement & - & Promising \\
\texttt{kholodna2024activelearning} & Kholodna et al. (2024) & Information Extraction (NER/NLI) & classify & f1 & - & Promising \\
\texttt{kim2024meganno} & Kim et al. (2024) & Information Extraction (NER/NLI) & classify & f1 & - & Promising \\
\texttt{nasution2024chatgptlabel} & Nasution \& Onan (2024) & Information Extraction (NER/NLI) & classify & accuracy & - & Mixed \\
\texttt{ner2024augment} & Naraki et al. (2024) & Information Extraction (NER/NLI) & classify & f1 & - & Promising \\
\texttt{nli2024labeldist} & Chen et al. (2024) & Information Extraction (NER/NLI) & classify & pearson & - & Promising \\
\texttt{ronningstad2024gptannotator} & Ronningstad et al. (2024) & Information Extraction (NER/NLI) & classify & f1 & - & Mixed \\
\texttt{qiu2025labelensemble} & Qiu et al. (2025) & Information Extraction (NER/NLI) & classify & accuracy & - & Promising \\
\texttt{zhou2023ifeval} & Zhou et al. (2023) & Instruction Following & verify & accuracy & - & Validated \\
\texttt{zeng2024llmbar} & Zeng et al. (2024) & Instruction Following & pairwise & accuracy & - & Mixed \\
\texttt{ifcritic2025} & Wen et al. (2025) & Instruction Following & classify & pct\_agreement & - & Promising \\
\texttt{legaldocrec2025} & Pradhan et al. (2025) & Legal & ranking & spearman & 0.73 & Promising \\
\texttt{lemaj2025} & Enguehard et al. (2025) & Legal & pointwise & pct\_agreement & - & Mixed \\
\texttt{kocmi2023gemba} & Kocmi \& Federmann (2023) & Machine Translation & pointwise & kendall & - & Promising \\
\texttt{kocmi2023gembamqm} & Kocmi \& Federmann (2023) & Machine Translation & verify & pct\_agreement & 0.96 & Validated \\
\texttt{lu2023erroranalysis} & Lu et al. (2023) & Machine Translation & verify & kendall & - & Promising \\
\texttt{sun2023radimpressions} & Sun et al. (2023) & Medicine \& Clinical & pointwise & pct\_agreement & - & Caution \\
\texttt{tang2023medevidence} & Tang et al. (2023) & Medicine \& Clinical & pointwise & pct\_agreement & - & Caution \\
\texttt{brain2024radgpt} & Mitsuyama et al. (2024) & Medicine \& Clinical & classify & accuracy & 0.94 & Mixed \\
\texttt{brake2024clinicalnote} & Brake \& Schaaf (2024) & Medicine \& Clinical & pointwise & pct\_agreement & - & Mixed \\
\texttt{wang2024clinicalevent} & Wang et al. (2024) & Medicine \& Clinical & classify & pct\_agreement & - & Promising \\
\texttt{chung2025verifact} & Chung et al. (2025) & Medicine \& Clinical & verify & pct\_agreement & - & Mixed \\
\texttt{clinstruct2025} & Brake et al. (2025) & Medicine \& Clinical & pointwise & icc & 0.82 & Mixed \\
\texttt{croxford2025autoeval} & Croxford et al. (2025) & Medicine \& Clinical & pointwise & pct\_agreement & - & Mixed \\
\texttt{croxford2025clinsummjudge} & Croxford et al. (2025) & Medicine \& Clinical & pointwise & pct\_agreement & - & Mixed \\
\texttt{healthbench2025} & Arora et al. (OpenAI) (2025) & Medicine \& Clinical & pointwise & pct\_agreement & - & Promising \\
\texttt{kim2025emulate} & Kim \& Kim (2025) & Medicine \& Clinical & pointwise & pct\_agreement & - & Mixed \\
\texttt{llmevalmed2025} & Zhang et al. (2025) & Medicine \& Clinical & pointwise & pct\_agreement & - & Mixed \\
\texttt{szymanski2025limits} & Szymanski et al. (2025) & Medicine \& Clinical & pairwise & pct\_agreement & 0.66 & Caution \\
\texttt{clindialog2026} & Sun et al. (2026) & Medicine \& Clinical & pointwise & pct\_agreement & - & Mixed \\
\texttt{frenchmedqa2026} & Belmadani et al. (2026) & Medicine \& Clinical & pointwise & kappa & - & Mixed \\
\texttt{medjudge2026scoping} & Li et al. (2026) & Medicine \& Clinical & review & nan & - & Caution \\
\texttt{counselbench2025} & Li et al. (2025) & Mental Health & pointwise & pct\_agreement & - & Caution \\
\texttt{hua2025mhscoping} & Hua et al. (2025) & Mental Health & review & nan & - & Caution \\
\texttt{mhtrust2025} & Badawi et al. (2025) & Mental Health & pointwise & icc & - & Mixed \\
\texttt{mhsupport2026} & Badawi et al. (2026) & Mental Health & pointwise & icc & - & Mixed \\
\texttt{liu2023trustworthy} & Liu et al. (2023) & Methodology \& Bias & survey & nan & - & Mixed \\
\texttt{saito2023verbositybias} & Saito et al. (2023) & Methodology \& Bias & pairwise & pct\_agreement & - & Caution \\
\texttt{wang2023shepherd} & Wang et al. (2023) & Methodology \& Bias & pointwise & pct\_agreement & - & Promising \\
\texttt{zhu2023judgelm} & Zhu et al. (2023) & Methodology \& Bias & pairwise & pct\_agreement & - & Promising \\
\texttt{bavaresco2024judgebench} & Bavaresco et al. (2024) & Methodology \& Bias & classify & kappa & 0.28 & Mixed \\
\texttt{chen2024humansorllms} & Chen et al. (2024) & Methodology \& Bias & pairwise & pct\_agreement & - & Caution \\
\texttt{desmond2024evalullm} & Desmond et al. (2024) & Methodology \& Bias & pointwise & pct\_agreement & - & Mixed \\
\texttt{fan2024sedareval} & Fan et al. (2024) & Methodology \& Bias & pointwise & pct\_agreement & - & Promising \\
\texttt{feuer2024style} & Feuer et al. (2024) & Methodology \& Bias & pairwise & pct\_agreement & - & Caution \\
\texttt{gu2024survey} & Gu et al. (2024) & Methodology \& Bias & survey & nan & - & Mixed \\
\texttt{jung2024trustescalate} & Jung et al. (2024) & Methodology \& Bias & pairwise & pct\_agreement & - & Promising \\
\texttt{justice2024prejudice} & Ye et al. (2024) & Methodology \& Bias & pairwise & pct\_agreement & - & Caution \\
\texttt{ke2024critiquellm} & Ke et al. (2024) & Methodology \& Bias & pointwise & spearman & - & Mixed \\
\texttt{koo2024cobbler} & Koo et al. (2024) & Methodology \& Bias & pairwise & winrate\_corr & 0.44 & Caution \\
\texttt{li2024compsurvey} & Li et al. (2024) & Methodology \& Bias & survey & nan & - & Mixed \\
\texttt{li2024gen2judge} & Li et al. (2024) & Methodology \& Bias & survey & nan & - & Mixed \\
\texttt{li2024splitmerge} & Li et al. (2024) & Methodology \& Bias & pairwise & pct\_agreement & - & Mixed \\
\texttt{liu2024pairwisepref} & Liu et al. (2024) & Methodology \& Bias & pairwise & pct\_agreement & - & Promising \\
\texttt{pan2024hcdjudge} & Pan et al. (2024) & Methodology \& Bias & pointwise & nan & - & Mixed \\
\texttt{panickssery2024selfpref} & Panickssery et al. (2024) & Methodology \& Bias & pairwise & pct\_agreement & - & Caution \\
\texttt{raina2024robust} & Raina et al. (2024) & Methodology \& Bias & pointwise & pct\_agreement & - & Unreliable \\
\texttt{shankar2024validators} & Shankar et al. (2024) & Methodology \& Bias & pointwise & pct\_agreement & - & Mixed \\
\texttt{stureborg2024inconsistent} & Stureborg et al. (2024) & Methodology \& Bias & pointwise & pct\_agreement & - & Caution \\
\texttt{thakur2024judgingjudges} & Thakur et al. (2024) & Methodology \& Bias & pairwise & pct\_agreement & - & Mixed \\
\texttt{wataoka2024selfpref} & Wataoka et al. (2024) & Methodology \& Bias & pairwise & pct\_agreement & - & Caution \\
\texttt{zhu2024nationalitybias} & Zhu et al. (2024) & Methodology \& Bias & pointwise & pct\_agreement & - & Caution \\
\texttt{calderon2025alttest} & Calderon et al. (2025) & Methodology \& Bias & classify & pct\_agreement & - & Promising \\
\texttt{gao2025nlgsurvey} & Gao et al. (2025) & Methodology \& Bias & survey & nan & - & Mixed \\
\texttt{gao2025reranking} & Gao et al. (2025) & Methodology \& Bias & ranking & kendall & - & Mixed \\
\texttt{hu2025trainjudge} & Hu et al. (2025) & Methodology \& Bias & pointwise & pct\_agreement & - & Promising \\
\texttt{huang2025empiricaljudge} & Huang et al. (2025) & Methodology \& Bias & pointwise & pct\_agreement & - & Mixed \\
\texttt{judgesverdict2025} & Han et al. (2025) & Methodology \& Bias & pointwise & kappa & - & Promising \\
\texttt{li2025prefleakage} & Li et al. (2025) & Methodology \& Bias & pairwise & pct\_agreement & - & Caution \\
\texttt{murugadoss2025evaltheeval} & Murugadoss et al. (2025) & Methodology \& Bias & pointwise & pct\_agreement & - & Mixed \\
\texttt{voutsa2025biaseddesign} & Voutsa et al. (2025) & Methodology \& Bias & classify & pct\_agreement & - & Caution \\
\texttt{yamauchi2025designchoices} & Yamauchi et al. (2025) & Methodology \& Bias & pointwise & pct\_agreement & - & Mixed \\
\texttt{imrit2026iaa} & James et al. (2026) & Methodology \& Bias & review & krippendorff\_alpha & - & Mixed \\
\texttt{temperature2026} & Li et al. (2026) & Methodology \& Bias & pointwise & pct\_agreement & - & Mixed \\
\texttt{khondaker2023gptaraeval} & Khondaker et al. (2023) & Multilingual & classify & f1 & - & Caution \\
\texttt{mmeval2024} & Son et al. (2024) & Multilingual & pairwise & accuracy & - & Mixed \\
\texttt{multiljudge2025} & Fu et al. (2025) & Multilingual & pointwise & pct\_agreement & - & Caution \\
\texttt{reliablemulti2026} & Zubiaga et al. (2026) & Multilingual & pointwise & pct\_agreement & - & Caution \\
\texttt{chen2024mllmjudge} & Chen et al. (2024) & Multimodal (Vision-Language) & pairwise & pct\_agreement & 0.79 & Mixed \\
\texttt{duan2024uimockup} & Duan et al. (2024) & Multimodal (Vision-Language) & pointwise & pct\_agreement & - & Mixed \\
\texttt{lee2024promvision} & Lee et al. (2024) & Multimodal (Vision-Language) & pointwise & pearson & - & Mixed \\
\texttt{lu2024wildvision} & Lu et al. (2024) & Multimodal (Vision-Language) & pairwise & pct\_agreement & - & Promising \\
\texttt{yasunaga2025mmrewardbench} & Yasunaga et al. (2025) & Multimodal (Vision-Language) & pairwise & accuracy & 0.72 & Caution \\
\texttt{chatgptreviewers2024} & Ho et al. (2024) & Peer Review \& Science & pointwise & pct\_agreement & 0.07 & Caution \\
\texttt{liang2024feedback} & Liang et al. (2024) & Peer Review \& Science & pointwise & pct\_agreement & - & Mixed \\
\texttt{murad2024quality} & Tarakji et al. (2024) & Peer Review \& Science & classify & pct\_agreement & 0.61 & Mixed \\
\texttt{prismascreen2024} & Guo et al. (2024) & Peer Review \& Science & classify & kappa & 0.91 & Validated \\
\texttt{rose2025rob} & Rose et al. (2025) & Peer Review \& Science & classify & kappa & - & Mixed \\
\texttt{shopovski2025peerreview} & Shopovski et al. (2025) & Peer Review \& Science & pointwise & pct\_agreement & - & Mixed \\
\texttt{guo2023howclose} & Guo et al. (2023) & QA \& Factuality & pointwise & pct\_agreement & - & Mixed \\
\texttt{min2023factscore} & Min et al. (2023) & QA \& Factuality & verify & pct\_agreement & - & Promising \\
\texttt{li2024pedants} & Li et al. (2024) & QA \& Factuality & verify & pct\_agreement & - & Promising \\
\texttt{madaan2024refverdict} & Reference-Guided Verdict authors (2024) & QA \& Factuality & pointwise & pct\_agreement & - & Promising \\
\texttt{wei2024safe} & Wei et al. (2024) & QA \& Factuality & verify & pct\_agreement & 0.72 & Promising \\
\texttt{leas2023contentanalysis} & Leas et al. (2023) & Qualitative Coding & classify & pct\_agreement & - & Mixed \\
\texttt{meng2024chalet} & Meng et al. (2024) & Qualitative Coding & classify & pct\_agreement & - & Mixed \\
\texttt{qualigpt2024} & Zhang et al. (2024) & Qualitative Coding & classify & pct\_agreement & - & Mixed \\
\texttt{mehta2025qualgenai} & Mehta et al. (2025) & Qualitative Coding & classify & pct\_agreement & - & Mixed \\
\texttt{qualcoding2025jla} & Xiao et al. (2025) & Qualitative Coding & classify & fleiss\_kappa & 0.46 & Mixed \\
\texttt{thematic2025charity} & Wen et al. (2025) & Qualitative Coding & classify & pct\_agreement & - & Mixed \\
\texttt{es2023ragas} & Es et al. (2023) & RAG & pointwise & pct\_agreement & - & Mixed \\
\texttt{saadfalcon2023ares} & Saad-Falcon et al. (2023) & RAG & classify & accuracy & - & Promising \\
\texttt{jin2024ragreward} & Jin et al. (2024) & RAG & pairwise & accuracy & - & Mixed \\
\texttt{raju2024calc2adj} & Raju et al. (2024) & Reasoning \& Math & verify & accuracy & - & Mixed \\
\texttt{tan2024judgebench} & Tan et al. (2024) & Reasoning \& Math & pairwise & accuracy & 0.55 & Caution \\
\texttt{mathrobust2026} & Yosef et al. (2026) & Reasoning \& Math & verify & accuracy & - & Mixed \\
\texttt{lee2023rlaif} & Lee et al. (2023) & Reward Modeling & pairwise & pct\_agreement & - & Mixed \\
\texttt{lambert2024rewardbench} & Lambert et al. (2024) & Reward Modeling & pairwise & accuracy & - & Mixed \\
\texttt{wu2024metarewarding} & Wu et al. (2024) & Reward Modeling & pairwise & pct\_agreement & - & Mixed \\
\texttt{yuan2024selfrewarding} & Yuan et al. (2024) & Reward Modeling & pairwise & pct\_agreement & - & Mixed \\
\texttt{ifreward2026} & Wen et al. (2026) & Reward Modeling & ranking & kendall & 0.61 & Caution \\
\texttt{belal2023sentiment} & Belal et al. (2023) & Sentiment \& Emotion & classify & accuracy & - & Promising \\
\texttt{koptyra2023clarinemo} & Koptyra et al. (2023) & Sentiment \& Emotion & classify & pct\_agreement & - & Mixed \\
\texttt{zhang2023sentiment} & Zhang et al. (2023) & Sentiment \& Emotion & classify & accuracy & - & Mixed \\
\texttt{niu2024text2emotion} & Niu et al. (2024) & Sentiment \& Emotion & classify & pct\_agreement & - & Mixed \\
\texttt{aldeen2023chatgptvshuman} & Aldeen et al. (2023) & Social-Science Annotation & classify & accuracy & - & Mixed \\
\texttt{cegin2023paraphrases} & Cegin et al. (2023) & Social-Science Annotation & classify & pct\_agreement & - & Mixed \\
\texttt{gilardi2023chatgpt} & Gilardi et al. (2023) & Social-Science Annotation & classify & accuracy & - & Validated \\
\texttt{ollion2023mindhype} & Ollion et al. (2023) & Social-Science Annotation & classify & pct\_agreement & - & Caution \\
\texttt{ostyakova2023crowdexperts} & Ostyakova et al. (2023) & Social-Science Annotation & classify & pct\_agreement & - & Mixed \\
\texttt{pangakis2023validation} & Pangakis et al. (2023) & Social-Science Annotation & classify & f1 & 0.71 & Mixed \\
\texttt{reiss2023testing} & Reiss (2023) & Social-Science Annotation & classify & pct\_agreement & - & Caution \\
\texttt{wu2023llmworkers} & Wu et al. (2023) & Social-Science Annotation & classify & pct\_agreement & - & Mixed \\
\texttt{zhu2023reproduce} & Zhu et al. (2023) & Social-Science Annotation & classify & pct\_agreement & - & Mixed \\
\texttt{li2024stance} & Li \& Conrad (2024) & Social-Science Annotation & classify & pct\_agreement & - & Mixed \\
\texttt{pangakis2024keephumans} & Pangakis \& Wolken (2024) & Social-Science Annotation & classify & f1 & - & Promising \\
\texttt{ziems2024css} & Ziems et al. (2024) & Social-Science Annotation & classify & accuracy & - & Mixed \\
\texttt{ahmad2025moralmachine} & Ahmad \& Takemoto (2025) & Social-Science Annotation & classify & pct\_agreement & - & Mixed \\
\texttt{horych2025promisespitfalls} & Horych et al. (2025) & Social-Science Annotation & classify & f1 & - & Mixed \\
\texttt{tornberg2025political} & Törnberg (2025) & Social-Science Annotation & classify & accuracy & - & Validated \\
\texttt{gao2023humanlike} & Gao et al. (2023) & Summarization & pointwise & spearman & - & Mixed \\
\texttt{liu2023geval} & Liu et al. (2023) & Summarization & pointwise & spearman & 0.51 & Promising \\
\texttt{luo2023factinconsistency} & Luo et al. (2023) & Summarization & verify & pct\_agreement & - & Mixed \\
\texttt{shen2023notyet} & Shen et al. (2023) & Summarization & pointwise & spearman & - & Caution \\
\texttt{lee2024unisumeval} & Lee et al. (2024) & Summarization & pointwise & pct\_agreement & - & Promising \\
\texttt{song2024finesure} & Song et al. (2024) & Summarization & verify & pct\_agreement & - & Promising \\
\texttt{tang2024tofueval} & Tang et al. (2024) & Summarization & verify & pct\_agreement & - & Caution \\
\texttt{zhang2024newssumm} & Zhang et al. (2024) & Summarization & pointwise & pct\_agreement & - & Promising \\
\texttt{wu2023hpsv2} & Wu et al. (2023) & Text-to-Image & pointwise & accuracy & - & Promising \\
\texttt{lin2024vqascore} & Lin et al. (2024) & Text-to-Image & pointwise & pearson & - & Promising \\
\bottomrule
\end{longtable}