\footnotesize
\begin{longtable}{@{}l l l l c l@{}}
\caption{Study 2 corpus (55 studies): HCC/HCI/qualitative methods using LLMs vs human input.}\label{tab:study2full}\\
\toprule
Study & Method & Role & Community & Agree & Verdict \\
\midrule
\endfirsthead
\toprule Study & Method & Role & Community & Agree & Verdict \\ \midrule \endhead
Chew et al. (2023) & Content analysis & augment & CSS & -- & Promising \\
Leas et al. (2023) & Content analysis & augment & Health & -- & Mixed \\
Long et al. (2024) & Content analysis & augment & Education & -- & Mixed \\
Dunivin (2025) & Content analysis & augment & CSS & -- & Promising \\
Anderson et al. (2024) & Creativity/ideation & augment & HCI & -- & Caution \\
Gilardi et al. (2023) & Crowdsourced annotation & replace & CSS & -- & Validated \\
Tornberg (2023) & Crowdsourced annotation & replace & CSS & -- & Validated \\
Kuzman et al. (2023) & Crowdsourced annotation & replace & NLP & -- & Mixed \\
Li et al. (2023) & Crowdsourced annotation & augment & NLP & -- & Promising \\
Ostyakova et al. (2023) & Crowdsourced annotation & replace & NLP & -- & Mixed \\
Tabone \& de Winter (2023) & HCI research methods & augment & HCI & -- & Mixed \\
Aubin Le Quere et al. (2024) & HCI research methods & augment & HCI & -- & Mixed \\
Salminen et al. (2024) & Persona generation & augment & HCI & -- & Mixed \\
Jung et al. (2025) & Persona generation & augment & HCI & -- & Mixed \\
Haxvig et al. (2025) & Persona generation & replace & HCI & -- & Caution \\
Zhang et al. (2023) & Qual analysis (general) & augment & Qual-methods & -- & Mixed \\
Wachinger et al. (2024) & Qual analysis (general) & augment & Health & -- & Mixed \\
Li et al. (2024) & Qual analysis (general) & augment & Health & 0.40 & Mixed \\
Mehta et al. (2025) & Qual analysis (general) & augment & Qual-methods & -- & Mixed \\
Davison et al. (2024) & Qual analysis (meta) & augment & CSS & -- & Caution \\
Schroeder et al. (2025) & Qual analysis (meta) & augment & HCI & -- & Mixed \\
Zhang et al. (2024) & Qual analysis (tool) & augment & HCI & -- & Mixed \\
Meng et al. (2024) & Qual analysis (tool) & augment & HCI & -- & Mixed \\
Xiao et al. (2023) & Qual coding (deductive) & augment & HCI & -- & Promising \\
Savelka et al. (2023) & Qual coding (deductive) & augment & NLP & -- & Mixed \\
Zhang et al. (2025) & Qual coding (deductive) & augment & Qual-methods & 0.46 & Mixed \\
authors (2025) & Qual coding (deductive) & augment & Qual-methods & 0.46 & Mixed \\
Gao et al. (2024) & Qual coding (inductive) & augment & HCI & -- & Promising \\
Dunivin (2024) & Qual coding (inductive) & replace & Qual-methods & -- & Promising \\
Ngo et al. (2026) & Qual coding (inductive) & augment & HCI & -- & Mixed \\
Wu et al. (2023) & Social-computing annotation & replace & CSCW & -- & Mixed \\
Zhu et al. (2023) & Social-computing annotation & replace & CSCW & -- & Mixed \\
Rajashekar et al. (2024) & Social-computing annotation & augment & HCI & -- & Mixed \\
Argyle et al. (2023) & Synthetic participants & simulate & CSS & -- & Mixed \\
Bisbee et al. (2023) & Synthetic participants & replace & CSS & -- & Caution \\
Cheng et al. (2023) & Synthetic participants & simulate & NLP & -- & Caution \\
Wang et al. (2024) & Synthetic participants & replace & HCI & -- & Caution \\
Bail (2024) & Synthetic participants & simulate & CSS & -- & Mixed \\
Abbasiantaeb et al. (2024) & Synthetic participants & simulate & IR & -- & Mixed \\
Huang et al. (2025) & Synthetic participants & simulate & CSS & -- & Mixed \\
Salminen et al. (2025) & Synthetic participants & replace & HCI & -- & Caution \\
De Paoli (2023) & Thematic analysis & augment & CSS & -- & Mixed \\
Dai et al. (2023) & Thematic analysis & augment & NLP & -- & Promising \\
Prescott et al. (2024) & Thematic analysis & augment & Health & -- & Mixed \\
Nguyen-Trung (2025) & Thematic analysis & augment & Qual-methods & -- & Mixed \\
Jain et al. (2025) & Thematic analysis & replace & Qual-methods & 0.91 & Promising \\
Castellanos et al. (2025) & Thematic analysis & augment & Health & 0.80 & Promising \\
Sharma et al. (2025) & Thematic analysis & augment & HCI & -- & Promising \\
Wen et al. (2025) & Thematic analysis & augment & Qual-methods & -- & Mixed \\
Kocaballi (2023) & UX/design critique & augment & HCI & -- & Mixed \\
Duan et al. (2024) & UX/design critique & augment & HCI & -- & Mixed \\
Duan et al. (2024) & UX/design critique & augment & HCI & -- & Mixed \\
Duan et al. (2024) & UX/design critique & augment & HCI & -- & Mixed \\
Guerino et al. (2025) & Usability/heuristic eval & replace & HCI & 0.21 & Caution \\
Zhong et al. (2025) & Usability/heuristic eval & replace & HCI & 0.75 & Mixed \\
\bottomrule
\end{longtable}