\appendix

% =====================================================================
\section{Review protocol and reliability rubric}\label{app:protocol}
% =====================================================================
\paragraph{Identification.} Both reviews follow PRISMA~2020. The primary bibliographic source is the
\textbf{OpenAlex} API; we cross-check with the \textbf{Semantic Scholar} Graph API and a structured
\textbf{web ``deep-research''} arm. Study~1a used a 59-query web protocol plus venue-scoped sweeps; Study~2 used a
25-query HCC/HCI/qualitative concept-block protocol (the same query strings were issued against every source so the
arms are comparable). Concept blocks combine an LLM term (``LLM'', ``large language model'', ``GPT-4'', ``ChatGPT'',
``Gemini''), an evaluation/agreement term (``LLM-as-a-judge'', ``automatic evaluation'', ``annotation'', ``inter-annotator
agreement'', ``human evaluation''), and, for Study~2, an HCC method term (``qualitative coding'', ``thematic analysis'',
``content analysis'', ``crowdsourcing'', ``participant simulation'', ``persona'', ``usability evaluation'', ``design
critique''). Records were deduplicated by DOI and normalized title.

\paragraph{Screening and eligibility.} \emph{Inclusion:} peer-reviewed or preprint studies that empirically compare
LLM judgments to human judgments on the same items and report (or allow computing) an agreement statistic.
\emph{Exclusion:} non-empirical position papers, studies with no human baseline, studies that use LLMs only to
generate (not judge) content, and off-topic retrievals. Title/abstract screening was followed by full-text
eligibility assessment; per-stage counts appear in the PRISMA flow figures (Figures~\ref{fig:prisma1}
and~\ref{fig:s2prisma}).

\paragraph{Reliability verdict (five-level rubric).} Each study is coded against the \emph{human-human agreement
ceiling} for its task:
\begin{itemize}[leftmargin=1.4em,itemsep=1pt]
\item \textbf{1 Validated:} LLM-human agreement is at or above the human-human ceiling (substitution is empirically
justified).
\item \textbf{2 Promising:} agreement approaches the ceiling under specific, reported conditions (model, prompt,
aggregation); conditional substitution.
\item \textbf{3 Mixed:} results are task- or setup-dependent and inconsistent across studies.
\item \textbf{4 Caution:} agreement is consistently and materially below the ceiling.
\item \textbf{5 Unreliable:} agreement is near chance or dominated by bias (position, verbosity, self-preference).
\end{itemize}
We report a reliability score $=6-\text{verdict}$ and synthesize within metric families (e.g.\ Cohen's $\kappa$,
Krippendorff's $\alpha$, Spearman $\rho$, accuracy) rather than pooling incommensurable effect sizes. The full coded
corpora (Appendices~\ref{app:s1} and~\ref{app:s2}) are released for re-coding.

% =====================================================================
\section{Study 1b: G-Eval replication details}\label{app:s1bdetail}
% =====================================================================
We replicate the summary-level G-Eval protocol \citep{liu2023geval} on SummEval \citep{fabbri2021summeval}
($100$ source articles $\times$ $16$ system summaries $=1600$ summaries, each with expert means for four aspects).
Each (summary, aspect) pair is scored $1$ to $5$ by the judge with the aspect criterion below; we then compute the
\textbf{summary-level Spearman} $\rho$ (per source document, correlate the judge's $16$ scores with the human means,
averaged over documents, dropping documents with no score variance) and compare it to the reported G-Eval-4/GPT-4
correlations. Judges are the four most powerful open models in the available open-model catalogue
(\texttt{glm-5.1-fp8}~$754$B, \texttt{deepseek-v4-pro}, \texttt{gptoss-120b}, \texttt{qwen3.6-35b-a3b-fp8}), decoded
at temperature~$0$. Aspect criteria (verbatim):
\begin{quote}\small
\textbf{Coherence (1-5):} the collective quality of all sentences; the summary should be well-structured and
well-organized, building from sentence to sentence into a coherent body of information, not just a heap of related
information.\\[2pt]
\textbf{Consistency (1-5):} factual alignment between the summary and the source; a consistent summary contains only
statements entailed by the source document; hallucinated or unsupported facts are penalized.\\[2pt]
\textbf{Fluency (1-5):} the quality of individual sentences (grammar, capitalization, readability).\\[2pt]
\textbf{Relevance (1-5):} selection of the most important content from the source; redundancy and unimportant
content are penalized.
\end{quote}
The judge receives the source article and the summary and returns only a JSON object \verb|{"score": <1-5>}| (a
larger token budget and a retry handle reasoning-model outputs). In total Study~1b contributes \ONEnjudg{} judgments.

% =====================================================================
\section{Study 3: datasets, judging prompts, and metrics}\label{app:s3detail}
% =====================================================================
\paragraph{Datasets.} Table~\ref{tab:cards} summarizes the six datasets. Each is sampled to $n{=}500$ items with a
clear majority label (ties dropped); we use the per-item annotator distributions to compute the human ceiling.

\begin{table}[h]\centering\small
\caption{Study 3 dataset cards. Ceiling $=$ random-annotator-vs-majority accuracy. Contam.\ $=$ max verbatim-recall
tier across probed judges.}
\label{tab:cards}
\begin{tabular}{@{}l l l c c c@{}}
\toprule
Dataset & Task & Source & Annot./item & Ceiling & Contam. \\
\midrule
ChaosNLI-SNLI & NLI (3-way) & SNLI + ChaosNLI relabels & ${\sim}100$ & 0.75 & MEDIUM \\
ChaosNLI-MNLI & NLI (3-way) & MultiNLI + ChaosNLI relabels & ${\sim}100$ & 0.64 & MEDIUM \\
GoEmotions & sentiment (4-way) & Reddit (Google) & ${\sim}3$-$5$ & 0.78 & MEDIUM \\
SBIC & offensiveness (binary) & Social Bias Frames & ${\sim}3$ & 0.91 & MEDIUM \\
HateXplain & hate speech (3-way) & Twitter/Gab & $3$ & 0.83 & MEDIUM \\
MultiPICo & irony (binary) & Reddit/Twitter (2024) & $3$-$8$ & 0.82 & LOW/MED \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Judging prompts.} Each model judges every item as a virtual annotator under instructions paralleling the
human guidelines, returning a JSON label on the final line (parsed with a surface-form-to-code map). The exact user
prompts:
\begin{quote}\small\ttfamily
NLI: Premise: \{premise\} / Hypothesis: \{hypothesis\} / Does the premise ENTAIL the
hypothesis, CONTRADICT it, or is it NEUTRAL? -> \{"label": "entailment"|"neutral"|"contradiction"\}\\[2pt]
Hate: Post: \{text\} / Classify: HATE SPEECH (attacks/dehumanizes a group based on
identity), OFFENSIVE (abusive but not group-targeted), or NORMAL. -> \{"label":
"hate speech"|"offensive"|"normal"\}\\[2pt]
Emotion: Comment: \{text\} / Overall sentiment: POSITIVE, NEGATIVE, AMBIGUOUS
(mixed/uncertain), or NEUTRAL. -> \{"label": "positive"|"negative"|"ambiguous"|"neutral"\}\\[2pt]
Offensive: Post: \{text\} / Is this post offensive (including potentially offensive)?
-> \{"label": "offensive"|"not offensive"\}\\[2pt]
Irony: \{post+reply\} / Is the REPLY ironic/sarcastic (conveys a meaning different from
or opposite to its literal content), or not ironic? -> \{"label": "ironic"|"not ironic"\}
\end{quote}

\paragraph{Metrics.} Let an item have $A$ human annotations with majority label $y^\star$.
\textbf{Human ceiling} is the random-annotator-vs-majority accuracy (the expected agreement of one held-out human
with the majority), averaged over items; we also report the pairwise human-human agreement. \textbf{Accuracy},
\textbf{Cohen's $\kappa$}, and \textbf{macro-F1} are computed against $y^\star$. The \textbf{alt-test} winning rate
\citep{calderon2025alttest} is the fraction of annotators for whom replacing that human with the LLM does not reduce
agreement with the remaining humans (a count-based leave-one-annotator-out test); a winning rate $\ge0.5$ is the bar
for claiming the LLM can ``replace'' a human. The \textbf{jury} is the per-item majority vote of the model panel
\citep{verga2024poll}. \textbf{95\% confidence intervals} are nonparametric bootstrap (1000 item resamples).
\textbf{Power:} at $n{=}500$ the accuracy CI half-width is $\le\pm4.4\%$ and the design has $>80\%$ power to detect a
$0.10$ gap from the ceiling. \textbf{Contamination probe:} the judge is given the dataset name and a prefix
($\approx$ one third) of an item's text and asked to reproduce the remainder verbatim; we report the mean normalized
sequence overlap and flag HIGH ($>0.6$ mean or $>20\%$ near-verbatim), MEDIUM ($>0.35$ mean), or LOW. Only item-level
labels and aggregates are released (no raw text); the runs recorded \emph{zero} API errors and a 100\% answer-parse
rate across all \STHRn{} judgments.

\paragraph{Inferential model.} The mixed-effects analysis models each judgment's correctness
($\mathbf{1}[\text{judge}=y^\star]$) with fixed effects for task subjectivity ($1-$ceiling, dataset level) and model
scale ($\log_{10}$ parameters), reported as a Bayesian logistic GLMM with random intercepts for dataset and item and,
for clean inference, as a logistic GLM with item-cluster-robust standard errors; the Benjamini-Hochberg procedure
controls the false-discovery rate across the \SMEfdrtests{} judge$\times$dataset ceiling-gap tests. A naive
two-predictor version of this model overstates a ``subjectivity'' effect; once construct granularity and label
base-rate skew are added and item-cluster-robust standard errors are used, subjectivity is not significant
($\mathrm{OR}=\GLMsubjOR$, $p=\GLMsubjP$) and the robust predictors are base-rate skew, scale, and granularity. A
dataset-level meta-regression ($n{=}\metaN$) is reported with leave-one-dataset-out bounds.

% =====================================================================
\section{Inter-coder reliability}\label{app:irr}
% =====================================================================
Because the reliability verdict and the role/stance codes embed judgement, we re-coded a held-out random sample of
each corpus with two \emph{independent} coders who saw only the per-study summaries and the rubric (no original
codes, no other context). For Study~1a ($n{=}\IRRsoneN$, 25\%) the verdict reproduced at Krippendorff
$\alpha=\IRRsoneA$ (ordinal, three coders) with \IRRsoneWone\% of cases within one level. For Study~2
($n{=}\IRRstwoN$, 30\%) the verdict gave $\alpha=\IRRstwoV$, the augment/replace/simulate role $\alpha=\IRRstwoRole$,
and the epistemic stance $\alpha=\IRRstwoStance$ (the least reliable code). \emph{Caveat:} the re-coders are
LLM-assisted, like the primary pipeline, so these figures measure rubric \emph{reproducibility} under independent
application, not human inter-rater agreement; the moderate stance $\alpha$ is why we treat stance-based claims as
indicative.

% =====================================================================
\section{Robustness and validity checks}\label{app:robust}
% =====================================================================
\textbf{Prompt robustness.} We re-ran a subset of Study~3 (three models $\times$ six datasets, $n{=}120$) under
three semantically equivalent prompt paraphrases per task. \emph{Accuracy} is fairly prompt-stable (mean SD across
paraphrases $=\PRmeanSD$), but the discrete five-level \emph{verdict} is exactly stable in only \PRstable{}/\PRtotal{}
cells: most instability is a one-level flip for cells sitting near a band boundary, and the smaller model is the most
sensitive (worst-case acc SD $\PRmaxSD$), the larger models the least. We therefore report verdicts as robust to
\emph{within one level} rather than exact, and flag small-model verdicts on subjective tasks as prompt-sensitive.
\textbf{Contamination clean control.} We ran the verbatim-recall probe on freshly authored, post-cutoff sentences
that no model can have seen. The result is a cautionary one: the high-recall model still scores $\CCmaxOverlap$ mean
overlap (\CCflag) on this guaranteed-clean text, i.e.\ it confabulates plausible continuations regardless of
memorization, while the low-recall model scores LOW. The probe thus has a high false-positive rate for high-recall
models and \emph{cannot} be read as a reliable leakage test; the uniform MEDIUM tiers in Table~\ref{tab:study3} are
largely an artifact of generative fluency. We retain the probe only as a conservative, low-recall-model signal and
base our substantive claims on the disagreement analysis instead.
\textbf{Annotator-subgroup check.} On MultiPICo (which carries annotator demographics), the panel's agreement with
the female- vs male-annotator majority differs by only \MPCgenderGap, i.e.\ we did not detect a large majority-group
bias in this corpus, though demographic metadata is sparse and this check is limited.

% =====================================================================
\section{Study 1 corpus}\label{app:s1}
% =====================================================================
{\footnotesize\input{tables/tab_full_studies}}

% =====================================================================
\section{Study 2 corpus}\label{app:s2}
% =====================================================================
\input{tables/tab_study2_full}
