\appendix

% =====================================================================
\section{Review protocol and reliability rubric}\label{app:protocol}
% =====================================================================
\paragraph{Identification.} The review follows PRISMA~2020. The primary bibliographic source is the \textbf{OpenAlex} API; we cross-check with the \textbf{Semantic Scholar} Graph API and a structured \textbf{web ``deep-research''} arm (a 59-query protocol plus venue-scoped sweeps). Concept blocks combine an LLM term (``LLM'', ``large language model'', ``GPT-4'', ``ChatGPT'', ``Gemini'') with an evaluation/agreement term (``LLM-as-a-judge'', ``automatic evaluation'', ``annotation'', ``inter-annotator agreement'', ``human evaluation''). Records were deduplicated by DOI and normalized title.

\paragraph{Screening and eligibility.} \emph{Inclusion:} peer-reviewed or preprint studies that empirically compare
LLM judgments to human judgments on the same items and report (or allow computing) an agreement statistic.
\emph{Exclusion:} non-empirical position papers, studies with no human baseline, studies that use LLMs only to
generate (not judge) content, and off-topic retrievals. Title/abstract screening was followed by full-text
eligibility assessment; per-stage counts appear in the PRISMA flow figures (Figure~\ref{fig:prisma1}).

\paragraph{Reliability verdict (five-level rubric).} Each study is coded against the \emph{human-human agreement
ceiling} for its task:
\begin{itemize}[leftmargin=1.4em,itemsep=1pt]
\item \textbf{1 Validated:} LLM-human agreement is at or above the human-human ceiling (substitution is empirically
justified).
\item \textbf{2 Promising:} agreement approaches the ceiling under specific, reported conditions (model, prompt,
aggregation); conditional substitution.
\item \textbf{3 Mixed:} results are task- or setup-dependent and inconsistent across studies.
\item \textbf{4 Caution:} agreement is consistently and materially below the ceiling.
\item \textbf{5 Unreliable:} agreement is near chance or dominated by bias (position, verbosity, self-preference).
\end{itemize}
We report a reliability score $=6-\text{verdict}$ and synthesize within metric families (e.g.\ Cohen's $\kappa$,
Krippendorff's $\alpha$, Spearman $\rho$, accuracy) rather than pooling incommensurable effect sizes. The full coded corpus (Appendix~\ref{app:s1}) is released for re-coding.

% =====================================================================
\section{Study 2: G-Eval replication details}\label{app:s1bdetail}
% =====================================================================
We replicate the summary-level G-Eval protocol \citep{liu2023geval} on SummEval \citep{fabbri2021summeval}
($100$ source articles $\times$ $16$ system summaries $=1600$ summaries, each with expert means for four aspects).
Each (summary, aspect) pair is scored $1$ to $5$ by the judge with the aspect criterion below; we then compute the
\textbf{summary-level Spearman} $\rho$ (per source document, correlate the judge's $16$ scores with the human means,
averaged over documents, dropping documents with no score variance) and compare it to the reported G-Eval-4/GPT-4
correlations. Judges are the four most powerful open models in the available open-model catalogue
(\texttt{glm-5.1-fp8}~$754$B, \texttt{deepseek-v4-pro}, \texttt{gptoss-120b}, \texttt{qwen3.6-35b-a3b-fp8}), decoded
at temperature~$0$. Aspect criteria (verbatim):
\begin{quote}\small
\textbf{Coherence (1-5):} the collective quality of all sentences; the summary should be well-structured and
well-organized, building from sentence to sentence into a coherent body of information, not just a heap of related
information.\\[2pt]
\textbf{Consistency (1-5):} factual alignment between the summary and the source; a consistent summary contains only
statements entailed by the source document; hallucinated or unsupported facts are penalized.\\[2pt]
\textbf{Fluency (1-5):} the quality of individual sentences (grammar, capitalization, readability).\\[2pt]
\textbf{Relevance (1-5):} selection of the most important content from the source; redundancy and unimportant
content are penalized.
\end{quote}
The judge receives the source article and the summary and returns only a JSON object \verb|{"score": <1-5>}| (a
larger token budget and a retry handle reasoning-model outputs). In total Study~1b contributes \ONEnjudg{} judgments.

% =====================================================================
\section{Study 3: datasets, judging prompts, and metrics}\label{app:s3detail}
% =====================================================================
\paragraph{Datasets.} Study 3 uses the \NLIndat{} ChaosNLI datasets (Table~\ref{tab:cardsnli}); each is sampled to
$n{=}500$ items with a clear majority label (ties dropped), and the ${\sim}100$ human labels per item give a precise
human ceiling.

\begin{table}[h]\centering\small
\caption{Study 3 (NLI) dataset cards. Ceiling $=$ random-annotator-vs-majority accuracy.}
\label{tab:cardsnli}
\input{tables/tab_cards_nli}
\end{table}

\paragraph{Models.} Table~\ref{tab:modelsA} lists the judge panel. Anonymized identifiers map to open-weight families; exact checkpoint identifiers, revisions, and quantization are released in the non-anonymous version.
\begin{table}[h]\centering\small
\caption{Judge panel (Studies 2--3).}\label{tab:modelsA}
\input{tables/tab_models}
\end{table}

\paragraph{Judging prompt.} Each model labels every item as a virtual annotator, returning a JSON label on the final
line (parsed with a surface-form-to-code map):
\begin{quote}\small\ttfamily
Premise: \{premise\} / Hypothesis: \{hypothesis\} / Does the premise ENTAIL the hypothesis, CONTRADICT it, or is it
NEUTRAL? -> \{"label": "entailment"|"neutral"|"contradiction"\}
\end{quote}

\paragraph{Metrics.} Let an item have $A$ human annotations with majority label $y^\star$. \textbf{Human ceiling} is
the random-annotator-vs-majority accuracy (expected agreement of one held-out human with the majority), averaged over
items; we also report pairwise human agreement, and bootstrap its 95\% CI by resampling annotators within items.
\textbf{Accuracy}, \textbf{Cohen's $\kappa$}, and \textbf{macro-F1} are against $y^\star$; the \textbf{jury} is the
per-item panel majority \citep{verga2024poll}; \textbf{95\% CIs} are nonparametric bootstrap (1000 item resamples).
\textbf{Contamination screen:} the judge is given the dataset name and a one-third prefix of an item and asked to
reproduce the remainder; we report mean normalized overlap, but a clean-control (Appendix~\ref{app:robust}) shows it
false-positives on high-recall models, so we treat it as a conservative screen. The run recorded \emph{zero} API
errors and a 100\% answer-parse rate across all \NLInjudg{} judgments.

\paragraph{Inferential model.} We model each judgment's correctness ($\mathbf{1}[\text{judge}=y^\star]$) with an
item-level Bayesian logistic GLMM with random intercepts for item and model, and report the variance components on a
common logit scale (item $\mathrm{SD}_{\text{logit}}=\NLIitemSDlogit$, model $\NLImodelSDlogit$). With two datasets
we do not fit a dataset-level model. To test whether the accuracy decline on high-disagreement items is a label-noise
artifact, we bin items by human entropy and report the judge-vs-ceiling \emph{gap} per bin (it is near zero
throughout for NLI, see the main text).

% =====================================================================
\section{Inter-coder reliability}\label{app:irr}
% =====================================================================
Because the reliability verdict and the role/stance codes embed judgement, we re-coded a held-out random sample of
each corpus with two \emph{independent} coders who saw only the per-study summaries and the rubric (no original
codes, no other context). For the review ($n{=}\IRRsoneN$, a 25\% sample) the reliability verdict reproduced at
Krippendorff $\alpha=\IRRsoneA$ (ordinal, three coders) with \IRRsoneWone\% of cases within one level.
\emph{Caveat:} the re-coders are
LLM-assisted, like the primary pipeline, so these figures measure rubric \emph{reproducibility} under independent
application, not human inter-rater agreement; the moderate stance $\alpha$ is why we treat stance-based claims as
indicative.

% =====================================================================
\section{Robustness and validity checks}\label{app:robust}
% =====================================================================
\textbf{Prompt robustness.} We re-ran a robustness subset (three models, $n{=}120$ per cell) under
three semantically equivalent prompt paraphrases per task. \emph{Accuracy} is fairly prompt-stable (mean SD across
paraphrases $=\PRmeanSD$), but the discrete five-level \emph{verdict} is exactly stable in only \PRstable{}/\PRtotal{}
cells: most instability is a one-level flip for cells sitting near a band boundary, and the smaller model is the most
sensitive (worst-case acc SD $\PRmaxSD$), the larger models the least. We therefore report verdicts as robust to
\emph{within one level} rather than exact, and flag small-model verdicts on subjective tasks as prompt-sensitive.
\textbf{Contamination clean control.} We ran the verbatim-recall probe on freshly authored, post-cutoff sentences
that no model can have seen. The result is a cautionary one: the high-recall model still scores $\CCmaxOverlap$ mean
overlap (\CCflag) on this guaranteed-clean text, i.e.\ it confabulates plausible continuations regardless of
memorization, while the low-recall model scores LOW. The probe thus has a high false-positive rate for high-recall
models and \emph{cannot} be read as a reliable leakage test; the uniform MEDIUM tiers in Table~\ref{tab:nlires} are
largely an artifact of generative fluency. We retain the probe only as a conservative, low-recall-model signal and
base our substantive claims on the disagreement analysis instead.
\textbf{Annotator-subgroup check.} On MultiPICo (which carries annotator demographics), the panel's agreement with
the female- vs male-annotator majority differs by only \MPCgenderGap, i.e.\ we did not detect a large majority-group
bias in this corpus, though demographic metadata is sparse and this check is limited.
\textbf{Ceiling vs annotator count.} The random-annotator-vs-majority ceiling depends on how many annotators an item
has: subsampling ChaosNLI-SNLI (${\sim}100$ annotators) to $A{=}3$ raises its estimated ceiling from
\RTwoablCeilFull{} to \RTwoablCeilThree{} (fewer annotators yield more unanimous majorities). We therefore compute
each dataset's ceiling at its \emph{native} annotator count and caution that ceilings are not directly comparable
across datasets with very different $A$; the disagreement-aware analyses (entropy, $\kappa$) do not depend on this
estimator.

% =====================================================================
\section{Study 1 corpus}\label{app:s1}
% =====================================================================
{\footnotesize\input{tables/tab_full_studies}}

% =====================================================================
