% =====================================================================
\section{Discussion}
% =====================================================================
\subsection{Review and experiment agree}
The review and the experiment tell one story. The field positions LLMs to \emph{augment} rather than replace humans,
with reliability ordered augment $>$ replace $>$ simulate; the experiment shows why that ordering is correct for the
field's central labeling case. On subjective social-computing constructs, open judges do not reach the human-human
ceiling, and their errors are not random: they concentrate on the items where humans themselves disagree. The
binding constraint is therefore not model capability but the contested human reference, which is exactly the
property that makes these constructs ``human-centered'' in the first place.

\subsection{Connections to HCI and measurement scholarship}
Three HCI conversations are sharpened by this evidence. \textbf{(1) There is no single ground truth.} CSCW and HCI
have long argued that inter-rater reliability is a negotiated practice, not a natural fact
\citep{mcdonald2019reliability}, and NLP has reframed annotator disagreement as signal \citep{aroyo2015truth,
plank2022humanlabel}; benchmarking against the human ceiling makes the judges' ``failures'' legible as properties of
the construct, not fixable model deficits. \textbf{(2) Interpretation is not labeling.} Reflexive thematic analysis
treats coding as situated interpretation \citep{braun2006thematic}, and qualitative scholars warn that ``conditional
trust'' in LLM output hollows out rigor \citep{schroeder2025usestensions,davison2024ethics}; the augment-not-replace
consensus and the empirical shortfall are two views of the same boundary. \textbf{(3) Participants are not
simulable.} The ``silicon sample'' program \citep{argyle2023outofone} meets a growing critique that simulated
participants flatten identity \citep{wang2024flatten,cheng2023compost,bisbee2023perils,salminen2025syntheticcritical};
our finding that judges default to majority readings and lose the minority signal is that flattening at the level of
a single subjective label, a representational harm a single accuracy number conceals \citep{fricker2007epistemic,
birhane2022values}.

\subsection{A critical assessment for the field}
We name two risks the community should track, marking what our data support and what extends prior critique.
\textbf{False closure (data-grounded).} Reporting one accuracy against a majority gold imposes consensus where the
data shows disagreement; our irony case (0.82 accuracy at $\kappa{=}0.40$) shows how a headline number masks
base-rate learning. \textbf{Monoculture and deskilling (conjecture).} Cheap labeling invites substituting LLM
judgment for the human annotation and reflexive interpretation that train researchers; combined with the documented
convergence of judges toward crowd rather than expert consensus \citep{bavaresco2024judgebench} and the way
technical framings abstract away the social context of measurement \citep{selbst2019abstraction,suchman2007humanmachine},
this could erode the field's interpretive capacity. We offer it as a hypothesis, not a finding.

\subsection{A decision framework for HCC}
\begin{itemize}[leftmargin=1.4em,itemsep=2pt]
\item \textbf{Automate (with light audit):} objective annotation of user-generated content (stance, topic, frames)
where the human ceiling is high and verifiable \citep{gilardi2023chatgpt,tornberg2023political}.
\item \textbf{Augment, human-in-the-loop:} subjective coding and thematic/content analysis: use the LLM for
first-pass coding, breadth, and disagreement surfacing, but keep human interpretive authority, calibrate on a
labeled subset, and report chance-corrected agreement against human coders \citep{gao2024collabcoder,dai2023llminloop}.
\item \textbf{Keep humans (do not substitute):} simulating participants or personas, and replacing expert
usability/design judgment, which flatten identity and forfeit situated knowledge
\citep{wang2024flatten,guerino2025gpt4ousability,salminen2025syntheticcritical}.
\end{itemize}
Practically, any HCC study reporting LLM-assisted analysis should state the LLM's \emph{role}, benchmark against a
\emph{human-human} baseline at the right granularity, report chance-corrected and disagreement-aware metrics with
uncertainty, evaluate on post-cutoff data where possible, and treat minority annotator readings as signal rather
than noise.
