\section{Ethics and reproducibility}
% =====================================================================
\textbf{Ethics.} The review analyzes published research, not human subjects, and Study 3 reuses already-public,
de-identified datasets under their licenses; this work was therefore not human-subjects research requiring IRB
review, and we sought an exemption determination consistent with our institution's policy. Two datasets (HateXplain,
SBIC) contain hateful or identity-attacking text, which we process only to measure moderation reliability and never
reproduce; to avoid redistributing harmful or personally-identifiable content we release only item-level labels and
aggregate statistics, never the raw texts. A deeper ethical point bears on our own method: by treating the
\emph{majority} human label as ``ground truth'' for the ceiling, we risk encoding majority-group bias and erasing
minority readings, exactly the harm we warn against. We mitigate this by (i) reporting the full disagreement (soft
labels, entropy) rather than only the majority, (ii) checking, where annotator demographics exist (MultiPICo), that
the panel does not agree disproportionately with one subgroup (gap $=\MPCgenderGap$; Appendix~\ref{app:robust}), and
(iii) recommending disagreement-aware evaluation in our guidance; we note the other corpora lack annotator
demographics, so this check is partial. The contamination probe is reported precisely so ``validated'' verdicts are
not silently inflated by pretraining exposure. The work is dual-use only in the benign sense that better-calibrated
LLM judges reduce the risk of unaccountable automated moderation; our central finding (that LLM judges should not replace humans on subjective social annotation) is itself a guard against premature deployment.
\textbf{Reproducibility.} Every number in this paper regenerates from released code: the OpenAlex, Semantic Scholar,
and web search logs; the coded corpus; the figure and table generators; the Study-2 judging/scoring/contamination/mixed-effects harness, all keyed to documented model identifiers served through
\PROVIDER{} at temperature~$0$ with idempotent, resumable checkpoints. The auto-generated statistics macros
mean the manuscript cannot drift from the data. Repository: \REPO{}.

% =====================================================================
